%-------------------------
% Resume in Latex
% Author : Thomas Ottaway adapted from Sourabh Bajaj's Template
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan, }
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingSimple}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small#2}\\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \text{\Large {Thomas Ottaway}} \\
  Github: \href{https://github.com/tottaway}{https://github.com/tottaway}\\
  Email : \href{mailto:thomas_ottaway@brown.edu}{thomas\_ottaway@brown.edu} \\
  Mobile : (518) 466-9711 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Brown University}{Providence, RI}
        {Applied Math-Computer Science GPA: 4.0}{Expected Graduation May 2022}
        \resumeItemListStart
            \resumeItem{Technical Coursework: }
            {Graduate Algorithms Seminar $\vert$ Sublinear Algorithms for Big Data $\vert$ Discrete Math $\vert$ Probability and Statistics $\vert$ Distributed Systems $\vert$ Convex Optimization $\vert$ Information Theory $\vert$ Dynamical Systems $\vert$ Operating Systems $\vert$ Control Systems Engineering}
        \resumeItemListEnd
   
    % \resumeSubheadingSimple{Albany High School}{Albany, NY}

    % \resumeSubheadingSimple
    %   {Independent Learning}{}
    %   \resumeItemListStart
    %     \resumeItem{}
    %       {Independent reading of computer vision research papers (primarily ResNets and variations such as Wide ResNets, Stochastic Depth, Pyramid nets etc.)}
    %   \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------Paid Experience---------------
\section{Work Experience}
  \resumeSubHeadingListStart
  \resumeSubheading{Draper Laboratories (Python, C++)}
    {Cambridge, MA}{Engineering Intern}{June 2020 - August 2020}
      \resumeItemListStart
        \resumeItem{}
        {Developed and implemented an algorithm to locate radiation sources using a mobile sensor. This included a particle filter to estimate the location and strength of the radiation source as well as information theoretic search heuristics for selecting new locations to take measurements.}
        \resumeItem{}
        {Implemented improved simulations for gaseous plumes and adapted search algorithm to estimate the source of the gas.}
      \resumeItemListEnd
      \resumeSubheading{NYS DOH/Health Research Institute (Python, SQL, JavaScript)}
    {Albany, NY}{Software Developer Intern}{Summer 2018 - Spring 2020}
      \resumeItemListStart
        \resumeItem{}
        {Migrated an application critical to the COVID-19 response effort from an Oracle back end to SQL Server}
        \resumeItem{}
        {Created systems to import patient identifying information as CSVs which drastically reduced data entry times}
        \resumeItem{}
        {Developed and maintained Python scripts to pre-process laboratory instrument data}
        \resumeItem{}
        {Interfaced with a legacy database containing 200+ tables}
        \resumeItem{}
        {Developed scripts for automated regression testing}
        % \resumeItem{}
        % {Built automated systems for HL7 message generation to expand Remote Order Entry accessibility}
      \resumeItemListEnd
    \resumeSubheadingSimple{Undergraduate Teaching Assistant for Discrete Math}
    {Jan. 2020 - May. 2020}
      \resumeItemListStart
        \resumeItem{}
        {Graded student assignments and held weekly office hours to explain concepts and help students with problems sets}
        {}
      \resumeItemListEnd
    \resumeSubheading{LingView (JavaScript, Node.js, React)}{Brown University}{Developer}{Sept. 2018 - May 2019}
      \resumeItemListStart
        \resumeItem{}
        {Built a front-end interface for viewing and searching through a linguistic corpus}
        % \resumeItem{}
        % {Collaborated with other students and faculty to determine project goals and priorities}
        % \resumeItem{}
        % {Explored various search technologies such as Fuse, LUNR, and SOLR}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----Projects and Volunteer Work-------
\section{Projects}
  \resumeSubHeadingListStart
\item \textbf{OS Kernel (C)} (\textit{Jan. 2020} - \textit{May 2020}) - Built a simple kernel with a scheduler, TTY driver, S5FS file system, and virtual memory as part of a course on Operating Systems.
\item \textbf{Ball Balancing (C++)} (\textit{May 2020}) - Built a high fidelity simulation of a table with two axis of rotation balancing a ball. Features included a rigid body physics simulator, a simulated raytraced camera, CV algorithms to estimate the ball's location, a Kalman Filter to smooth sensor noise, and tuned PID controller.
\item \textbf{Music Visualizer (Python)} (\textit{May 2020}) - Built a music visualizer using Fourier transforms.
\item \textbf{Neural Nets for Solving ODEs (Python)} (\textit{Aug. 2019}) Implemented some algorithms from \href{https://arxiv.org/abs/physics/9705023}{this paper}.
            % \resumeItem{}
            % {Implementing custom optimization algorithm with quadratic convergance}
\item \textbf{Rocket Stabilization (Python)} (\textit{Apr. 2019 - May 2019}) - Final group project for Nonlinear Dynamical Systems. We studied a thrust vector controlled rocket in two dimensions and discovered bifurcations which occurred as we varied the parameters of a PD controller.
        %   \resumeItemListEnd
        % \resumeSubheadingSimple
        %   {Exploring Numerical Methods}{Oct. 2018 - Apr. 2019}
        %   \resumeItemListStart
        %     \resumeItem{}
        %       {Explored algorithms for finding numerical approximations to differential equations using Python's numpy library}
        %     \resumeItem{}
        %       {Created visualizations for systems such as the 3-D wave equation and particles in chaotic systems}
        %   \resumeItemListEnd
    \resumeSubHeadingListEnd
% -------Skills--------
\section{Skills}
  \resumeSubHeadingListStart
    \item \textbf{Programming Languages} : Python, C++, C, JavaScript, Go, SQL, MATLAB
    % \item \textbf{Communication \& Adaptibility}: Ability to enter a team of diverse people, listen closely, and work collaboratively to push a project forward
    \item \textbf{Frameworks/Tools}: Numpy, Matplotlib, ROS, PyQtGraph, Django, SQLServer, Oracle, PyTorch, Gazebo
  \resumeSubHeadingListEnd
\section{Activities}
    \resumeSubHeadingListStart
    \item Juggling, running, rock climbing, cooking, blues dancing, unicycling, bicycling, playing piano
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
